Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms.tex
w/ DR's handwritten comments

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 (hereafter RXJ1131) at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry of the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$8 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the quasar host galaxy is an extended rotating disk, with a CO size of $R$$\sim$6\,kpc in radius and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
consistent with the optically-faint companion reported in previous studies.
We decompose the lensing-corrected total \bco line flux into two components and 
find a lensing-corrected gas mass of $M_{\rm gas}$\ssim1.4\E{10}\,\Msun for RXJ1131
and \ssim2\E{9}\,\Msun for the companion, corresponding
to a gas mass ratio of $\sim$7:1.
The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim1 reported in recent studies.
The lensing-corrected stellar mass $M_{*}$\ssim3\E{10}\,\Msun,
dust mass $M_{\rm dust}$\ssim4\E{8}\,\Msun, IR luminosity $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun, and 
star formation rate SFR$_{\rm FIR}$\eq120\pmm63 \sfrU of RXJ1131
together with its source-plane morphology of the gas and stellar populations
indicate ongoing star-formation activity that maybe as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of 0.27\petm{11}{8}\% that is higher
than the local value
but consistent with other galaxies at this epoch. Collectively, our results suggest
that the bulk of the black hole mass of RXJ1131 is already in place 
while its stellar bulge component is still assembling, and that its major mode of \SF is likely merger-driven.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to 
%our understanding of the
%processes governing the formation and evolution of both the SMBHs and their host galaxies.
% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution. 
% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}. 
It is currently not well-understood when and how the supermassive black holes (SMBHs) and 
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
only unresolved CO observations have been carried out for $\sim$$30$ ultra-luminous infrared galaxies (ULIRGs) up to date \citep{Combes11a, Combes13a}. %18+15

Meanwhile, empirical scaling relations such as the
$M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
has been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch
of \SF and AGN activity, have been made in recent years.
These studies find that 
% the $M_{\rm BH}$$/$$M_{\rm bulge}$ ratios of high-$z$ submillimeter galaxies (SMGs) 
% are lower than those of local AGN host galaxies \citep[\eg][]{Borys05a,Alexander08a}, 
% whereas those of high-$z$ quasar host galaxies 
% are higher than the local values \citep[\eg][]{Walter04a, McLure06a,Peng06a, Riechers08a,Coppin08a}, 
% suggesting that the co-eval growth of high-$z$ AGNs and their host galaxies follows different 
% timescales compared to their local counterparts. % different AGN mechanism, different AGN accretion rate
% However, any links between such fast-growing SMBHs and their host galaxies are not yet established at these high redshifts.
high-$z$ AGN host galaxies do not follow the same $M_{\rm BH}$$-$\mbulge relation \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained 
at intermediate redshifts.
This is owed to the difficulties in measuring stellar emission in optical quasar host galaxies, where
emission of quasars produces sidelobes that saturate the lower surface brightness starlight in the host galaxy,
or alternatively, due to the lack of spatially resolved CO observations to provide dynamical constraints on the stellar 
(bulge) mass.
With strong gravitational lensing, emission from the background quasar and its host galaxy originating from 
different source-plane locations and of different extent is being magnified and stretched out by different amount.
The lensed emission is therefore spatially resolved over more beams which reduces the sidelobes and enables 
measurements of the stellar emission in the host galaxy.

@@

In this paper, we present \bco and \cco line data observed towards RXJ1131 and
broadband photometry spanning rest-frame UV to radio wavelengths to 
study the properties of the molecular gas, the dust and stellar populations in the 
host galaxy of RXJ1131.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{HST}, we describe the astrometric corrections
applied to an image taken with the \hst ({\it HST}) by aligning it to
a radio image taken with the \vla (VLA).
In \Sec{results}, we report measurements of the \bco and \cco lines and broadband
photometry in RXJ1131.
In \Sec{anal}, we present dynamical lens modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss 
the ISM properties of the host galaxy of RXJ1131 and compare 
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively. 
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 10.0 MHz ($\sim$
$21.5$ \kms).  {\bf DR: DSB, 320 MHz/128 channels? <-> 2.5 MHz? I did not bin the data}
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
%
% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$35\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive.
The details of the observations can be found
in \citetalias{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is based on
its coordinates in the high-resolution optical image.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of 
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential}.
 \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of 
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, and also 
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

@@

We detect PdBI 2\,mm continuum emission, as shown in \Fig{cont}. The integrated flux density is
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy. Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved
emission towards the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and do not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map 
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy.
We note that this peak flux density is only our best estimate at the resolution of our observations, a non-negligible contribution from the background source to the total integrated (blended) flux may be present.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density 
% assumes that the foreground galaxy is a point source, the...

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved 
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Models of each slice thus provide information on
the corresponding kinematic component of the CO gas,
enabling us to reconstruct a velocity gradient in the source plane.
%
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.
%
The first use of a dynamical lens modeling approach is presented by \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
which is also the only other similar system whose host galaxy is lensed into an Einstein ring configuration.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5).
The spectra map covers an extent of $\sim$10"$\times$10"
centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
Spatial offset in arcsec is denoted in top left corner of each panel.
The velocity and flux density scales are denoted in the top right panel.
\label{fig:spatialSpec}}
\end{figure*}

@@

\subsection{\bco Kinematics}
Fitting two Gaussians with a single FWHM
to the ``intrinsic'' \bco line profile of RXJ1131 (after correcting for lensing using
the magnification factors for various channels and separating the emission from RXJ1131 and its companion),
we find a roughly symmetric double-horned profile with a flux ratio of 1.2\pmm0.4 between the peaks, which
are separated by
$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and each with a
FWHM of 220\pmm72\,\kms.
The peak separation obtained from this ``intrinsic'' line profile is
slightly lower than that obtained from the observed spectrum (\ie without lensing corrections).
This discrepancy is likely a result of differential lensing, which causes the line peak of the red wing
to shift towards higher velocity channels, and thereby biasing the centroid of
one Gaussian to higher velocity than otherwise.
To facilitate a comparison (\Sec{sizes}) with previous works, which were observed at lower spectral resolution,
we also fit a single-Gaussian to the intrinsic line profiles.
This yields FWHMs of 600\pmm160\,\kms for RXJ1131
and 73\pmm43\,\kms for the companion galaxy.

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 (hereafter RXJ1131) at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXJ1131 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXJ1131 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXJ1131 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, IR luminosity, and
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXJ1131.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% that is higher
than the local value
but consistent with other galaxies at this epoch, suggesting that the bulk of the black hole mass of RXJ1131 is already in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
%Studying the interplay between \SF and active galactic nucleus (AGN) activity across cosmic epochs is crucial to
%our understanding of the
%processes governing the formation and evolution of both the SMBHs and their host galaxies.
% Significant attention has been focused on studying the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs in recent studies of galaxy evolution.
% \citep{Wang10, Lamastra10, Hopkins+05, 06, DiMatteo+05a, Page11, Page12,Simpson12}
Many recent studies of galaxy evolution have been focused on investigating the interplay between star formation and active galactic nucleus (AGN) activity across cosmic epochs \citep[e.g.,][]{DiMatteo05a,Alexander05a,Hopkins06b,Coppin08a,Page12a,Simpson12a,Lamastra13a}.
It is currently not well-understood when and how the supermassive black holes (SMBHs) and
stellar populations of present-day massive galaxies were assembled,
but it is clear that the co-moving \SF rate and the black hole accretion rate densities both
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
A leading explanation for this decline is the decrease in molecular gas content and
\SF efficiency \citep[e.g.,][]{Erb06a, CW13, Walter14a},
but direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ that could confirm this explanation remain largely limited to
spatially unresolved CO observations of $\sim$$30$ ultra-luminous infrared galaxies \citep[ULIRGs; ][]{Combes11a, Combes13a}. %18+15

Meanwhile, empirical scaling relations such as the
$M_{\rm BH}$$-$\mbulge relation \citep[e.g.,][]{Magorrian98a, HR04a}
have been established locally, suggesting a co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch
of \SF and AGN activity, have been made in recent years.
These studies find that
high-$z$ AGN host galaxies do not appear to follow the same $M_{\rm BH}$$-$\mbulge relation as nearby spheroidal galaxies. \citep[\eg][]{Walter04a,Borys05a, McLure06a,Peng06a, Riechers08a,Coppin08a,Alexander08a}.
Yet, the $M_{\rm BH}$$-$\mbulge relation remains poorly-constrained
at intermediate redshifts.
This is owed to the difficulties in
measuring stellar emission in quasar host galaxies which is typically
saturated by the sidelobes from their quasars.
With strong gravitational lensing, emission from the background quasar and its host galaxy originating from
different source-plane locations with different spatial extent is being magnified and stretched out inhomogenously,
allowing their emission to be
spatially resolved over more beams to reduce the dynamic range, and thus 
measurements of the stellar emission in the host galaxy.

@@

In this paper, we present \bco and \cco line observations and
broadband photometry spanning rest-frame UV to radio wavelengths towards RXJ1131 to
study the properties of its molecular gas, the dust and stellar populations.
In \Sec{obs}, we outline details of the observations and of our data reduction procedures.
In \Sec{results}, we report results for the \bco and \cco emission and broadband
photometry in RXJ1131.
In \Sec{anal}, we present lens modeling and dynamical modeling of the \bco data and
spectral energy distribution (SED) modeling of the photometric data.
In \Sec{diss}, we discuss
the ISM properties of the host galaxy of RXJ1131 and compare
them to other galaxy populations at low and high redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = $69.32$ \kms Mpc\pmOne, $\Omega_{\rm M}$ = $0.29$, and
$\Omega_{\Lambda}$ = $0.71$ \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710 --> 3%
%
% amp de-correlation: % loss scales = 1- exp(-(50º*pi/180)^2 / 2) = ~32% loss
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$50$\degr$ over a baseline length of $\sim$135\,m.
We thus conservatively estimate
a calibration accuracy of $\sim$40\% based on the flux scale uncertainties,    % ~40 = usual CARMA ~15-20% + 35% add in quad
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat the derived \cco line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this paper do not rely on this quantity.

@@

\subsection{HST (Archival)}
We obtained an {\it HST} image taken with
the ACS
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive.
The details of the observations can be found
in \citetalias{Claeskens06a}.
We apply astrometric correction to the optical image by adopting the VLA 5\,GHz map as the
reference coordinate frame.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is based on
its coordinates in the high-resolution optical image.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em} 
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

@@

We detect 2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}). Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved
emission which we here assume to be dominated by the foreground galaxy. The peak flux (0.39\,$\pm$\,0.08\,mJy)
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). We therefore adopt
$S_{\nu}$ = 0.39\pmm0.08 mJy as the 2\,mm continuum emission towards
the background galaxy (RXJ1131).
The quoted uncertainty is from the flux measurement in the residual map and does not account for that in the de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...

@@

\subsection{Lens Modeling} \label{sec:lensmodel}
At the angular resolution of the \bco data, the source is resolved
$\gtrsim$2 resolution elements.
Given the extent of the lensed emission (see \Fig{CO21mom}),
this implies that we do not resolve
structures (e.g. knots and arcs) of the lensed emission
in our \bco data.
Nevertheless, the high spectral
resolution of these data provides dynamical information on
spatial scales smaller than the beam (see \Fig{CO21mom}).
Hence, we reconstruct the intrinsic gas dynamics  % - morphology of different kinematic components - velocity structure
by carrying out a parametric lens modeling over different
channel slices of the interferometric data using our lensing code
\uvmcmcfit
(\citealt{uvmcmcfit15a}; see \citealt{Bussmann15a} for details of the code).
Our approach is similar to \citet{Riechers08a}, who reconstruct a source-plane
velocity gradient and constrain the gas dynamics in a $z$\,$>$\,4 quasar PSS J2322$+$1944,
whose host galaxy is also lensed into an Einstein ring configuration.
To ensure adequate SNRs for lens modeling, we bin the frequency channels by a factor of five
to produce seven independent $\Delta v$\,$\sim$\,105\,\kms channels (dashed line in \Fig{delensed})
that cover the full linewidth of $\sim$750\,\kms.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{../Figures/spatialSpec_offsetShifted.eps}
\caption{
\bco spectrum as a function of position, binned by 3 pixels in each
direction (1\farcs5).
The spectra map covers an extent of $\sim$10''$\times$10''
centered on the pixel that corresponds to coordinates of the lensing galaxy ($\alpha_{\rm J2000}$\,=\,11$^{\rm h}$31$^{\rm m}$51\fs44, $\delta_{\rm J2000}$\,=\,$-$12\degr31\arcmin58\farcs3).
Spatial offset in arcsec is denoted in top left corner of each panel.
The velocity and flux density scales are denoted in the top right panel.
\label{fig:spatialSpec}}
\end{figure*}

@@

\subsection{\bco Kinematics}
Fitting two Gaussians with a common FWHM
to the ``intrinsic'' \bco line profile of RXJ1131 (after correcting for lensing using
the magnification factors for various channels and separating the emission from RXJ1131 and its companion),
we find a roughly symmetric double-horned profile with a flux ratio of 1.2\pmm0.4 between the peaks, which
are separated by
$\Delta v_{\rm sep}$ = 387\pmm45\,\kms, and each with a
FWHM of 220\pmm72\,\kms.
The peak separation obtained from this ``intrinsic'' line profile is
slightly lower than that obtained from the observed spectrum (\ie without lensing corrections).
This discrepancy is likely a result of differential lensing, which causes the line peak of the red wing
to shift towards higher velocity channels, and thereby biasing the centroid of
one Gaussian to higher velocity than otherwise.
To facilitate a comparison (\Sec{sizes}) with previous works, which were observed at lower spectral resolution,
we also fit a single-Gaussian to the intrinsic line profiles.
This yields FWHMs of 600\pmm160\,\kms for RXJ1131
and 73\pmm43\,\kms for the companion galaxy.

A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
are seen in \Fig{CO21mom}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of these data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content.
Therefore, in this scenario, RXJ1131 is
consistent with a disrupted disk galaxy hosting an optically
bright quasar and in the process of merging.
